### 2016-03-24 paper.tex
Use microtype package for improved typography
Interleaved Kay's monster theme section into the context section

\documentclass[a4paper]{article}                                     
\usepackage{url,xspace,epsfig,etoolbox}
\usepackage{natbib}
\usepackage{fullpage}
\usepackage[font=bf]{caption}
\usepackage{mdwlist}
\usepackage{graphicx}

@@

\section{Context}

Investigating the potential for culture-narration games to teach
cultural empathy brought our team into a partnership with
\textit{[a local library branch hidden for blind review]}. This branch
serves primarily patrons from low socio-economic status, although
its special technology education programs also draw homeschoolers from
around the region.
The youth patrons of the library tend to be 4rd--6th grade 
``latchkey kids'' who 
see the library as a place to visit with friends, to participate in programs,
and to access technology.

Conversations with program coordinators about culture-narration games
revealed that despite other differences, the youth patrons shared
a fascination with monsters, horror, and the macabre. 
This is in part because of cultural taboo: the youth will brag about
being able to see a PG-13-rated movie or play an M-rated game,
for example, and several kids worked together to produce an original
short movie based on battles between movie monsters.

The fascination exhibited by the youth patrons reflects various theses
of Cohen's monster theory~\citep{Cohen1996}. 
We see in their behavior that ``the same creatures who terrify and
interdict can evoke potent escapist fantasies''~(p.16).
Recognizing the youth patrons' attraction to this theme,
Cohen's theory establishing monsters as reflections of culture,
and the narrative potential of monsters,
our team decided to engage in a design experiment to validate our
hypotheses about culture-narration games,
in collaboration with \textit{the library branch}.

>>>>

\documentclass[a4paper]{article}
\usepackage{microtype}
\usepackage{url,xspace,epsfig,etoolbox}
\usepackage{natbib}
\usepackage{fullpage}
\usepackage[font=bf]{caption}
\usepackage{mdwlist}
\usepackage{graphicx}

@@

\section{Context and Theme}

Cultivating world culture empathy in children through narrative driven
gameplay begs for a theme that is inviting on multiple accounts. We
were drawn to the question of what our target audience looked for in
narration, in addition to what would serve as an aid in encouraging
world cultural empathy. 
We formed a partnership with \textit{[omitted for blind review]}, 
a non-lending branch that 
provides acommunity, training, and technology services in a
low socioeconomic area of our city.
The youth patrons of the library tend to be 4rd--6th grade 
``latchkey kids'' who 
see the library as a place to visit with friends, to participate in programs,
and to access technology.

Conversations with program coordinators about culture-narration games
revealed that despite other differences, the youth patrons shared a
fascination with monsters, horror, and the macabre.  This answer in
some ways seemed unsatisfactory: horror and empathy---cultural or
otherwise---do not seem to be a good match. Indeed, enjoying horror, when
viewed simply as enjoyment of others' pain, seems like the antithesis
of empathy. However, this love of horror, or the monstrous, can be
seen in our culture, touching down on all forms of media. Monsters has
been a hook for narratives throughout history. They have attracted
people of various walks of life, by playing into the fears of the
people.

\citeauthor{Cohen1996} draws attention to this in his book, 
\textit{Monster Theory}~\citeyear{Cohen1996}.
He offers a way of ``reading cultures through the monsters they
engender'' (p.~3).  Cohen notes that the conclusions we come to about
the cultures, from monsters or otherwise, will be a combination of
many fragments rather than a ``smooth epistemological whole.'' A monster
is brought about at a particular time and represents not only the
fears prevalent in the culture but also the values, that lead to that
fear (p.~4--12). Pinning that down is difficult. The monsters work more
as a ``snapshot'' of the culture at a particular moment than a
definition. This point is especially important for us to note when
creating a game whose goal is to encourage children's efforts to see
something from others' perspectives.
%Yet, we see in the children's behavior that ``the same creatures who terrify and interdict can evoke potent escapist fantasies''~(p.16).

For these reasons, monsters have become a staple theme for our
project. They were not only enticing to our target
audience---first observed by our community partner and later proven
through play testing---but also provide an excellent passage for
encouraging empathy, particularly cultural empathy. They represent
various cultures' sameness, in base forms of fear, yet difference, in
the ways that fear becomes specific and embodied. By encouraging an
understanding of both difference and sameness between cultures, they
encourage individuals to try to see something from someone else's
viewpoint.
